Unbiased pangenome graphs

### 2022-10-08 manuscript/main.tex
English tweaks

To compact $\mathcal{G}$, we traverse $Q$, finding each entry in $\mathcal{Z}$ in turn, recording its start and end in $\mathcal{V}$, which can be understood as a character vector or string containing all the sequence in the nodes of $\mathcal{G}$.
%in a ``graph vector'' $\mathcal{G} = v_1,v_2 \ldots v_{|\mathcal{V}|}$ containing the ordered characters of the graph.
%Any position in $\mathcal{G}$ so marked must be the start or end of a node.
We subsequently use these markings to subdivide $\mathcal{V}$ into a compacted version $\mathcal{V}'$ where compacted node boundaries are marked in a auxiliary bitvector $\mathcal{B} : |\mathcal{B}| = |\mathcal{V}|$ such that the first character in each compacted node is marked by a $1$ and other characters are marked $0$.
$\mathcal{B}$ allows us to compute compacted node ids using efficient rank operations \citep{Gog_2014}.
%such that $\forall_{i \in 1 \ldots |\mathcal{V}'|} |v_i| \ge 1$.
%In Algorithm \ref{alg:seqwish} we provide a detailed description of the graph induction algorithm.

@@

In contrast, \textit{minigraph} develops a kind of partial order alignment \citep{Lee_2002} over the minimizers (sparse $k$-mer set) of input genomes, and it progressively builds the graph by adding new variation from each genome in order.
We do expect it be order and reference (first input) biased, although the degree of bias requires experimentation to establish.

>>>>

To compact $\mathcal{G}$, we traverse $Q$, finding each entry in $\mathcal{Z}$ in turn, recording its start and end in $\mathcal{V}$, which can be understood as a character vector or string containing all the sequence in the nodes of $\mathcal{G}$.
%in a ``graph vector'' $\mathcal{G} = v_1,v_2 \ldots v_{|\mathcal{V}|}$ containing the ordered characters of the graph.
%Any position in $\mathcal{G}$ so marked must be the start or end of a node.
We subsequently use these markings to subdivide $\mathcal{V}$ into a compacted version $\mathcal{V}'$ where compacted node boundaries are marked in an auxiliary bitvector $\mathcal{B} : |\mathcal{B}| = |\mathcal{V}|$ such that the first character in each compacted node is marked by a $1$ and other characters are marked $0$.
$\mathcal{B}$ allows us to compute compacted node ids using efficient rank operations \citep{Gog_2014}.
%such that $\forall_{i \in 1 \ldots |\mathcal{V}'|} |v_i| \ge 1$.
%In Algorithm \ref{alg:seqwish} we provide a detailed description of the graph induction algorithm.

@@

In contrast, \textit{minigraph} develops a kind of partial order alignment \citep{Lee_2002} over the minimizers (sparse $k$-mer set) of input genomes, and it progressively builds the graph by adding new variation from each genome in order.
We do expect it to be order and reference (first input) biased, although the degree of bias requires experimentation to establish.
